---
title: "Time to event versus Logistic Regression"
author: "Hedwig Nora Nordlinder"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    highlight: tango
    code_folding: show
tags: [R, survival analysis]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10, 
  fig.height = 6,
  out.width = "100%"
)

# Load required packages
library(tidyverse)
library(knitr)
library(kableExtra)
```

## Introduction

Brief introduction to your blog post topic. What will readers learn? Why is this important?

## Data Preparation

```{r data-prep}
# Your data preparation code here
# Example:
# data <- read_csv("your_data.csv")
```

## Analysis

### Exploratory Data Analysis

```{r eda}
# Your exploratory analysis code here
```

### Key Findings

Discuss your main findings here. You can include:

- Important observations
- Unexpected results
- Practical implications

## Visualizations

```{r visualizations}
# Your visualization code here
# Example:
# ggplot(data, aes(x = x, y = y)) +
#   geom_point() +
#   theme_minimal()
```

## Conclusions

Summarize your key takeaways and potential next steps.

## References

<!-- If you're using citations, they'll appear here -->

## Session Info

```{r session-info}
sessionInfo()
```